**Bayesian statistics for longitudinal studies in biomedical research**

### 2020-11-09 Manuscripts/Manuscript_AM_v1.Rmd
Working on section 1

#### 1.2 Constant correlation

Missing observations, and correlation between measurements. How rm-ANOVA is limited by missing observations, and how both rm-ANOVA and LMEMs are limited with data that does not follow a linear trend (equations for both situations and the fit they produce.)
#### 1.1 Constant correlation

@@

#### 1.2 the case of LMEMs using splines and how they work and how they are better than rm-ANOVA

>>>>

_Question: How can one make a plot that tests the "limits" of the model, i.e how much "wiggliness" can this model accomodate? Make a plot to show the behavior of the model_

#### 1.2 Covariance and correlation

In a longitudinal study, multiple measures on the same subject creates a _correlation_ and _covariance_ issue that needs to be incorporated into the model. In this case, _correlation_ can be defined as the relationship between different variables, e.g. how much one variable changes when other variable changes. It can be further decomposed in _between-subject_ correlation and _within-subject correlation_. In the first case, _between-subject correlation_ measures the correlation between subject means, whereas _within-subject correlation_ describes how much a measurement in a subject changes in regard to another to another measurement _in the same subject_ [@roy2006].  between repeated measures on the same subject can be defined as the relationship between the variability . The _correlation_ of the measures can be practically defined as is defined as the relationship between  
Missing observations, and correlation between measurements. How rm-ANOVA is limited by missing observations, and how both rm-ANOVA and LMEMs are limited with data that does not follow a linear trend (equations for both situations and the fit they produce.)
#### 1.1 Constant correlation

@@

#### 1.2 the case of GMEMs using splines and how they work and how they are better than rm-ANOVA
